Full title of the paper (Capitalized)

### 2023-11-02 MDPI_submition.Rmd
Commit 2023-11-02 11:10

For completeness, we will provide below a brief overview of the 
<!--
[....Csid term is referenced above....]{.comment-start id="0" author="A N"
date="2023-07-15T20:00:52Z"} 
-->
clear sky identification algorithm (CSid),
<!--
[]{.comment-end id="0"} 
-->
along with the site specific thresholds.
To calculate the reference clear sky
$\text{SDR}_\text{CSref}$ we used the $\text{SDR}_\text{Haurwitz}$ derived by
the radiation model of @Haurwitz1945, adjusted for our site with a
factor $a$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process, as described
by @Long2000 and @Reno2016.
The target of
the optimization was the minimization of a function $f(a)$ (Eq.\ \ref{eq:minf}) and
was accomplished with the algorithmic function "optimise", which is an implementation based on the work of @Brent1973, from the library "stats" of the R programming language [@RCT2023]. 
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), 
<!--[....rephrased....]{.comment-start id="3" author="A N" date="2023-07-15T20:32:50Z"}-->
while the procedure, manages to characterize the majority of the data.
<!--[]{.comment-end id="3"}--> 
Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.

<!-- cost fuction -->
\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation}
where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is any of the tested clear sky radiation models.

<!-- adjusted Haurwitz -->
\begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = `r signif(alpha,3)` \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation}
where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{w}\,\text{m}^{-2}$ and $\theta$ is the solar zenith angle (SZA).

The criteria that were used to identify whether a measurement was taken
under clear-sky conditions are presented below.
A data point is flagged
as "clear-sky" if all criteria are satisfied, otherwise it is considered to be "cloud-sky".
Each criterion was applied
for a running window of $`r nt`$ consecutive one-minute measurements, and
the characterization is assigned to the central value of the window.
Each parameter, was calculated both from the observations and the
reference clear sky model, for each comparison.
The allowable range of variation is defined by the
model-derived value of the parameter multiplied by a factor plus an
offset. 
<!--[.... .expanded the description ....]{.comment-start id="4"
author="A N" date="2023-07-15T22:48:13Z"}
-->
The factors and the offsets were
determined empirically, by manual inspecting each filters performance on
selected days, and adjusting them accordingly, during an iterative
process.
<!--[[]{.comment-end id="4"}]{.insertion author="A N"
date="2023-07-15T22:48:13Z"}
-->

<!-- 1. MeanVIP -->
<!-- ### Mean value of irradiance during the time period. -->

<!--a) Mean of the measured $\overline{\text{SDR}}_i$ = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$ and running mean of the reference $\overline{\text{SDR}}_{\text{CSref},i}$ = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq. \ref{eq:MeanVIP}).-->

@@

## use kable
x_latex <- knitr::kable(spp,
                        format   = "latex",
                        booktabs = T,
                        escape   = T,
                        # format.args = list(digits = 3),
                        linesep  = "",
                        align    = "ccrr",
                        caption  = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")

x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c("striped",
                                    "hold_position")
    )

# position = "float_left"

@@

When making tables using `kable`, it is suggested to use
the `format="latex"` and `tabl.envir="table"` arguments
to ensure table numbering and compatibility with the mdpi
document class.

```{r tab1, echo=FALSE}
knitr::kable(mtcars[1:5, 1:3], 
             format = "latex", 
             booktabs = TRUE, 
             caption = "This is a table caption. Tables should be placed in the 
             main text near to the first time they are~cited.", 
             align = 'ccc', centering = FALSE,
             table.envir = "table", position = "H")
```

@@

This is an example of an equation:

$$
a = 1.
$$

>>>>

For completeness, we will provide below a brief overview of the 
<!--
[....Csid term is referenced above....]{.comment-start id="0" author="A N"
date="2023-07-15T20:00:52Z"} 
-->
clear sky identification algorithm (CSid),
<!--
[]{.comment-end id="0"} 
-->
along with the site specific thresholds.
To calculate the reference clear sky
$\text{SDR}_\text{CSref}$ we used the $\text{SDR}_\text{Haurwitz}$ derived by
the radiation model of @Haurwitz1945, adjusted for our site with a
factor $a$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process, as described
by @Long2000 and @Reno2016.
The target of
the optimization was the minimization of a function $f(a)$ (Eq.\ \ref{eq:minf}) and
was accomplished with the algorithmic function "optimise", which is an implementation based on the work of @Brent1973, from the library "stats" of the R programming language [@RCT2023]. 
The optimization and the selection of the clear sky reference model, was performed on SDR observations for the period 2016 - 2021.
During the optimization, eight simple clear sky radiation models were tested (Daneshyar-Paltridge-Proctor, Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel, Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by @Reno2012 and evaluated by @Reno2016.
We found, that Haurwitz's model, adjusted with the factor $a = `r signif(alpha,3)`$ yields one of the lowest root mean squared errors (RMSE), 
<!--[....rephrased....]{.comment-start id="3" author="A N" date="2023-07-15T20:32:50Z"}-->
while the procedure, manages to characterize the majority of the data.
<!--[]{.comment-end id="3"}--> 
Thus, our clear sky reference is derived by the Eq.\ \ref{eq:ahau}.
<!-- cost fuction -->
\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation}
where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is any of the tested clear sky radiation models.
<!-- adjusted Haurwitz -->
\begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = `r signif(alpha,3)` \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation}
where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $\text{w}\,\text{m}^{-2}$ and $\theta$ is the solar zenith angle (SZA).

The criteria that were used to identify whether a measurement was taken
under clear-sky conditions are presented below.
A data point is flagged
as "clear-sky" if all criteria are satisfied, otherwise it is considered to be "cloud-sky".
Each criterion was applied
for a running window of $`r nt`$ consecutive one-minute measurements, and
the characterization is assigned to the central value of the window.
Each parameter, was calculated both from the observations and the
reference clear sky model, for each comparison.
The allowable range of variation is defined by the
model-derived value of the parameter multiplied by a factor plus an
offset. 
<!--[.... .expanded the description ....]{.comment-start id="4"
author="A N" date="2023-07-15T22:48:13Z"}
-->
The factors and the offsets were
determined empirically, by manual inspecting each filters performance on
selected days, and adjusting them accordingly, during an iterative
process.
<!--[[]{.comment-end id="4"}]{.insertion author="A N"
date="2023-07-15T22:48:13Z"}
-->
<!-- 1. MeanVIP -->
<!-- ### Mean value of irradiance during the time period. -->
<!--a) Mean of the measured $\overline{\text{SDR}}_i$ = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{n}]$ and running mean of the reference $\overline{\text{SDR}}_{\text{CSref},i}$ = \text{mean}_{n=i-5}^{n=i+5}[\text{SDR}_{\text{CSref},n}]$ (Eq. \ref{eq:MeanVIP}).-->

@@

## use kable
x_latex <- knitr::kable(spp,
                        format      = "latex",
                        booktabs    = TRUE,
                        escape      = T,
                        # format.args = list(digits = 3),
                        linesep     = "",
                        align       = "ccrr",
                        centering   = FALSE,
                        table.envir = "table",
                        # position    = "H",
                        caption  = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")

x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c('striped', 'hold_position'), full_width = TRUE) %>%
    # kable_styling(full_width = T) %>%
    # kable_styling("striped")      %>%
    column_spec(1, width = "8em")

@@

<!-- When making tables using `kable`, it is suggested to use -->
<!-- the `format="latex"` and `tabl.envir="table"` arguments -->
<!-- to ensure table numbering and compatibility with the mdpi -->
<!-- document class. -->

<!-- ```{r tab1, echo=FALSE} -->
<!-- knitr::kable(mtcars[1:5, 1:3],  -->
<!--              format = "latex",  -->
<!--              booktabs = TRUE,  -->
<!--              caption = "This is a table caption. Tables should be placed in the  -->
<!--              main text near to the first time they are~cited.",  -->
<!--              align = 'ccc', centering = FALSE, -->
<!--              table.envir = "table", position = "H") -->
<!-- ``` -->

@@

### 2023-11-02 MDPI_submition.tex
Commit 2023-11-02 11:10

For completeness, we will provide below a brief overview of the clear
sky identification algorithm (CSid), along with the site specific
thresholds. To calculate the reference clear sky
\(\text{SDR}_\text{CSref}\) we used the \(\text{SDR}_\text{Haurwitz}\)
derived by the radiation model of \citet{Haurwitz1945}, adjusted for our
site with a factor \(a\) (Eq.~\ref{eq:ahau}), resulted by an iterative
optimization process, as described by \citet{Long2000} and
\citet{Reno2016}. The target of the optimization was the minimization of
a function \(f(a)\) (Eq.~\ref{eq:minf}) and was accomplished with the
algorithmic function ``optimise'', which is an implementation based on
the work of \citet{Brent1973}, from the library ``stats'' of the R
programming language \citep{RCT2023}. The optimization and the selection
of the clear sky reference model, was performed on SDR observations for
the period 2016 - 2021. During the optimization, eight simple clear sky
radiation models were tested (Daneshyar-Paltridge-Proctor,
Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel,
Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by \citet{Reno2012} and
evaluated by \citet{Reno2016}. We found, that Haurwitz's model, adjusted
with the factor \(a = 0.965\) yields one of the lowest root mean squared
errors (RMSE), while the procedure, manages to characterize the majority
of the data. Thus, our clear sky reference is derived by the
Eq.~\ref{eq:ahau}.

\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation} where: \(n\) is the total number of daylight records,
\(\text{SDR}_{\text{CSid},i}\) are the records identified as clear sky
by CSid, \(a\) is a hypothetical adjustment factor, and
\(\text{SDR}_{\text{testCSref},i}\) is any of the tested clear sky
radiation models.

\begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = 0.965 \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation} where: \(\text{SDR}_\text{CSref}\) is the reference clear
sky SDR, in \(\text{w}\,\text{m}^{-2}\) and \(\theta\) is the solar
zenith angle (SZA).

@@

@@

\caption{\label{tab:trendseasontable}\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\centering
\begin{tabular}[t]{ccrr}
\toprule
Sky condition & Season & Trend [\%/year] & Statistical signif. [\%]\\
\midrule
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{0.6860} & \cellcolor{gray!6}{99.9}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Cloudy sky} & Autumn & -0.4000 & 89.5\\
\bottomrule
\end{tabular}
\end{table}

@@

When making tables using \texttt{kable}, it is suggested to use the
\texttt{format="latex"} and \texttt{tabl.envir="table"} arguments to
ensure table numbering and compatibility with the mdpi document class.

\caption{\label{tab:tab1}This is a table caption. Tables should be placed in the 
             main text near to the first time they are~cited.}
\begin{tabular}[t]{lccc}
\toprule
  & mpg & cyl & disp\\
\midrule
Mazda RX4 & 21.0 & 6 & 160\\
Mazda RX4 Wag & 21.0 & 6 & 160\\
Datsun 710 & 22.8 & 4 & 108\\
Hornet 4 Drive & 21.4 & 6 & 258\\
Hornet Sportabout & 18.7 & 8 & 360\\
\bottomrule
\end{tabular}
\end{table}

@@

This is an example of an equation:

\[
a = 1.
\]

>>>>

For completeness, we will provide below a brief overview of the clear
sky identification algorithm (CSid), along with the site specific
thresholds. To calculate the reference clear sky
\(\text{SDR}_\text{CSref}\) we used the \(\text{SDR}_\text{Haurwitz}\)
derived by the radiation model of \citet{Haurwitz1945}, adjusted for our
site with a factor \(a\) (Eq.~\ref{eq:ahau}), resulted by an iterative
optimization process, as described by \citet{Long2000} and
\citet{Reno2016}. The target of the optimization was the minimization of
a function \(f(a)\) (Eq.~\ref{eq:minf}) and was accomplished with the
algorithmic function ``optimise'', which is an implementation based on
the work of \citet{Brent1973}, from the library ``stats'' of the R
programming language \citep{RCT2023}. The optimization and the selection
of the clear sky reference model, was performed on SDR observations for
the period 2016 - 2021. During the optimization, eight simple clear sky
radiation models were tested (Daneshyar-Paltridge-Proctor,
Kasten-Czeplak, Haurwitz, Berger-Duffie, Adnot-Bourges-Campana-Gicquel,
Robledo-Soler, Kasten and Ineichen-Perez), with a wide range of factors.
These models are described in more details by \citet{Reno2012} and
evaluated by \citet{Reno2016}. We found, that Haurwitz's model, adjusted
with the factor \(a = 0.965\) yields one of the lowest root mean squared
errors (RMSE), while the procedure, manages to characterize the majority
of the data. Thus, our clear sky reference is derived by the
Eq.~\ref{eq:ahau}. \begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation} where: \(n\) is the total number of daylight records,
\(\text{SDR}_{\text{CSid},i}\) are the records identified as clear sky
by CSid, \(a\) is a hypothetical adjustment factor, and
\(\text{SDR}_{\text{testCSref},i}\) is any of the tested clear sky
radiation models. \begin{equation}
\text{SDR}_\text{CSref} = a \times \text{SDR}_\text{Haurwitz} = 0.965 \times 1098 \times \cos(\theta) \times \exp \left( \frac{ - 0.057}{\cos(\theta)} \right) \label{eq:ahau}
\end{equation} where: \(\text{SDR}_\text{CSref}\) is the reference clear
sky SDR, in \(\text{w}\,\text{m}^{-2}\) and \(\theta\) is the solar
zenith angle (SZA).

@@

\begin{verbatim}
Usually it is recommended to use column_spec before collapse_rows, especially in LaTeX, to get a desired result. 
\end{verbatim}

@@

\caption{\label{tab:trendseasontable}\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\centering}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky condition & Season & Trend [\%/year] & Statistical signif. [\%]\\
\midrule
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{0.6860} & \cellcolor{gray!6}{99.9}\\

@@

\multirow{-4}{*}{\centering\arraybackslash Cloudy sky} & Autumn & -0.4000 & 89.5\\
\bottomrule
\end{tabu}
\end{table}

@@

@@
